The \dealii Library, Version 9.6

### 2024-09-25 9.6/paper.tex
Fix up a mistake.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
   \item The \texttt{FE\_NedelecSZ} class that contains our 
    implementation of the N\'ed\'elec element using the orientation 
    scheme of \cite{Zag06} now supports the computation of hanging 
    node constraints for locally refined, hexahedral meshes. 
    That is, the implementation of hanging node constraints now
    correctly addresses the sign-conflict that arises for $hp$ quadrilateral and 
    hexahedral N\'ed\'elec elements; 
    see \cite{Kinnewig2024} for details. 
    The other implementation of N\'ed\'elec elements, in the \texttt{FE\_NedelecSZ} class, already
    \todo[inline]{JPT: I think this should be \texttt{FE\_Nedelec}, without SZ?}
    implements hanging node constraints; therefore, there is no longer
    a difference for the user between the two classes as far as
    constraints are concerned. 
    However, the special case where, in 3D, more than four cells with 
    different refinement levels share a common edge is not covered yet.
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
   \item The \texttt{FE\_NedelecSZ} class that contains our 
    implementation of the N\'ed\'elec element using the orientation 
    scheme of \cite{Zag06} now supports the computation of hanging 
    node constraints for locally refined, hexahedral meshes. 
    That is, the implementation of hanging node constraints now
    correctly addresses the sign-conflict that arises for $hp$ quadrilateral and 
    hexahedral N\'ed\'elec elements; 
    see \cite{Kinnewig2024} for details. 
    The other implementation of N\'ed\'elec elements, in the \texttt{FE\_Nedelec} class, already
    implements hanging node constraints; therefore, there is no longer
    a difference for the user between the two classes as far as
    constraints are concerned. 
    However, the special case where, in 3D, more than four cells with 
    different refinement levels share a common edge is not covered yet.
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.
